Classical Mechanics Assignment X

### 2015-11-01 classical/latex/a3.tex
HI

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{marvosym} % Required for symbols in the colored box
\usepackage{ifsym} % Required for symbols in the colored box

@@

\allowdisplaybreaks

@@

\title{Classical Mechanics Assignment 3}
\author{Elliott Capek}
\titlespacing{\section}{0pt}{0pt}{5pt} % Spacing around titles

@@

\section{Problem One}
\textbf{Consider an object that is thrown vertically up with initial speed $v_0$ in a linear medium.} \\

@@

\begin{align*}
  m\ddot{y}(t) &= -mg - b\dot{y}(t)\\
  m\ddot{y}(t) &= -b\big(\frac{mg}{b} + \dot{y}(t))\\
  m\ddot{y}(t) &= -b\big(\dot{y}_{term} + \dot{y}(t))
  \hspace{1in}\ddot{y} = 0 \rightarrow \dot{y}_{term} = \frac{mg}{b}\\
  m\ddot{y}(t) &= -b\phi(t)
  \hspace{1.6in} \phi(t) = \dot{y}_{term} + \dot{y}(t)\\
  m\ddot{\phi(t)} &= -b\phi(t)
  \hspace{1.6in} \dot{\phi(t)} = \ddot{y}(t)\\
  \phi(t) &= Ae^{-\frac{bt}{m}}\\
  \dot{y}(t) &= Ae^{-\frac{b}{m}t} - \dot{y}_{term}
  \hspace{1.6in} \dot{y}(0) = \dot{y}_0 = A - \dot{y}_{term}\\
  \dot{y}(t) &= (\dot{y}_0 + \dot{y}_{term})e^{-\frac{b}{m}t} - \dot{y}_{term}\\
  \dot{y}(t) &= \dot{y}_0e^{-\frac{b}{m}t} + \dot{y}_{term}(e^{-\frac{b}{m}t} - 1)\\
  y(t) &= -\frac{m}{b}e^{-\frac{b}{m}t}\Big(\dot{y}_0 + \dot{y}_{term} \Big) - \dot{y}_{term}t\\
\end{align*}

@@

\begin{align*}
  \dot{y}(t) &= 0 = \dot{y}_0e^{-\frac{b}{m}t} + \dot{y}_{term}(e^{-\frac{b}{m}t} - 1)\\
  \dot{y}_{term}(1 - e^{-\frac{b}{m}t}) &= \dot{y}_0e^{-\frac{b}{m}t}\\
  \dot{y}_{term} - \dot{y}_{term}e^{-\frac{b}{m}t} &= \dot{y}_0e^{-\frac{b}{m}t}\\
  \dot{y}_{term}e^{\frac{b}{m}t} &= \dot{y}_0 + \dot{y}_{term}\\
  e^{\frac{b}{m}t} &= \frac{\dot{y}_0 + \dot{y}_{term}}{\dot{y}_{term}}\\
  t_{max} &= \frac{m}{b}\log{\frac{\dot{y}_0 + \dot{y}_{term}}{\dot{y}_{term}}}\\
  y(t_{max}) &= -\frac{m}{b}e^{-\frac{b}{m}\frac{m}{b}\log{\frac{\dot{y}_0 + \dot{y}_{term}}{\dot{y}_{term}}}}\Big(\dot{y}_0 + \dot{y}_{term} \Big) - \dot{y}_{term}\frac{m}{b}\log{\frac{\dot{y}_0 + \dot{y}_{term}}{\dot{y}_{term}}}\\
    y(t_{max}) &= -\frac{m}{b\frac{\dot{y}_0 + \dot{y}_{term}}{\dot{y}_{term}}}\Big(\dot{y}_0 + \dot{y}_{term} \Big) - \dot{y}_{term}\frac{m}{b}\log{\frac{\dot{y}_0 + \dot{y}_{term}}{\dot{y}_{term}}}\\
\end{align*}

\textbf{c. Show that the limiting case for very small drag coefficient coincides with the solution for the frictionless motion.}\\
For frictionless motion:
\begin{align*}
  \ddot{y}(t) &= -g\\
  \dot{y}(t) &= \dot{y}_0 - gt\\
  y(t) &= \dot{y}_0t - \frac{1}{2}gt^2\\
  \dot{y}(t_{max}) &= 0 \rightarrow t_{max} = \frac{\dot{y}}{g}\\
  y_{max} &= \frac{\dot{y}_0^2}{2g}\\
\end{align*}

For motion in a linear medium when $\lim_{b\rightarrow0}$:

\begin{align*}
  \lim_{b\rightarrow0}y(t_{max}) &= \lim_{b->0} \hspace{0.2cm} -\frac{m}{b\frac{\dot{y}_0 + \dot{y}_{term}}{\dot{y}_{term}}}\Big(\dot{y}_0 + \dot{y}_{term} \Big) - \dot{y}_{term}\frac{m}{b}\log{\frac{\dot{y}_0 + \dot{y}_{term}}{\dot{y}_{term}}}\\
  \lim_{b\rightarrow0}y(t_{max}) &= \lim_{b->0} \hspace{0.2cm} -\frac{m}{b\frac{\dot{y}_0 + \frac{mg}{b}}{\frac{mg}{b}}}\Big(\dot{y}_0 + \frac{mg}{b} \Big) - \frac{mg}{b}\frac{m}{b}\log{\frac{\dot{y}_0 + \frac{mg}{b}}{\frac{mg}{b}}}\\
  \lim_{b\rightarrow0}y(t_{max}) &= \lim_{b->0} \hspace{0.2cm} -\frac{m}{b\frac{\dot{y}_0 + \frac{mg}{b}}{\frac{mg}{b}}}\Big(\dot{y}_0 + \frac{mg}{b} \Big) - \frac{mg}{b}\frac{m}{b}\log{\frac{\dot{y}_0 + \frac{mg}{b}}{\frac{mg}{b}}}\\
\end{align*}

@@

\section{Problem Two}
\textbf{A point mass of mass m slides down an inclined plane under the influence of gravity. If the motion is resisted by a force $F=kmv^2$, show that the time required to move a distance d after starting from rest is:}

\begin{equation*}
  t = \frac{\cosh^{-1}(e^{kd})}{\sqrt{kg\sin(\Theta)}}\\
\end{equation*}

@@

We define a one-dimensional coordinate system where the positive axis points in the direction of motion of the point.\\

\begin{align*}
  \vec{F} &= \sin(\Theta)mg - kmv^2\\
  m\dot{v} &= \sin(\Theta)mg - kmv^2\\
  \frac{dv}{dt} &= \sin(\Theta)g - kv^2\\
  \frac{dv}{\sin(\Theta)g - kv^2} &= dt\\
  \int_0^{v} \frac{dv}{\sin(\Theta)g - kv^2} &= \int_0^t dt\\
  \int_0^{v} \frac{\csc(\Theta)}{g(1 - \frac{\csc(\Theta)k}{g}v^2)}dv &= \int_0^t dt\\
  \frac{\csc(\Theta)}{g}\int_0^{v} \frac{1}{1 - \frac{\csc(\Theta)k}{g}v^2}dv &= \int_0^t dt\\
  \frac{\csc(\Theta)}{g}\int_0^{v} \frac{1}{1 - \frac{\csc(\Theta)k}{g}v^2}dv &= \int_0^t dt
  \hspace{1in} u = \mathrm{i}v\sqrt{\frac{\csc(\Theta)k}{g}}\\
  -\frac{\csc(\Theta)}{g}\mathrm{i}\sqrt{\frac{g}{\csc(\Theta)k}}\int_0^{\mathrm{i}v\sqrt{\frac{\csc(\Theta)k}{g}}} \frac{1}{1 + u^2}du &= \int_0^t dt
  \hspace{1in} dv = -\mathrm{i}\sqrt{\frac{g}{\csc(\Theta)k}}du\\
  -\mathrm{i}\frac{\sqrt{\csc(\Theta)}}{\sqrt{kg}} \int_0^{\mathrm{i}v\sqrt{\frac{\csc(\Theta)k}{g}}} \frac{1}{1 + u^2}du &= \int_0^t dt\\
  -\mathrm{i}\frac{\sqrt{\csc(\Theta)}}{\sqrt{kg}} \tan^{-1}\Bigg(\mathrm{i}v\sqrt{\frac{\csc(\Theta)k}{g}}\Bigg) &= \int_0^t dt\\
  \frac{\sqrt{\csc(\Theta)}}{\sqrt{kg}} \tanh^{-1}\Bigg(v\sqrt{\frac{\csc(\Theta)k}{g}}\Bigg) &= t\\
  \frac{\tanh^{-1}\Bigg(v\sqrt{\frac{\csc(\Theta)k}{g}}\Bigg)}{\sqrt{kg\sin(\Theta)}} &= t\\ 
  \frac{\tanh^{-1}\Bigg(v\sqrt{\frac{\csc(\Theta)k}{g}}\Bigg)}{\sqrt{kg\sin(\Theta)}} &= t\\
  \tanh^{-1}\Bigg(v\sqrt{\frac{\csc(\Theta)k}{g}}\Bigg) &= t\sqrt{kg\sin(\Theta)}\\
  v\sqrt{\frac{\csc(\Theta)k}{g}} &= \tanh\Big(t\sqrt{kg\sin(\Theta)}\Big)\\
  v &= \frac{\tanh\Big(t\sqrt{kg\sin(\Theta)}\Big)}{\sqrt{\frac{\csc(\Theta)k}{g}}}\\    
\end{align*}

Now we try integrating out the v:

\begin{align*}
  d &= \int_0^t v(t) dt\\
  d &= \int_0^t \frac{\tanh\Big(t\sqrt{kg\sin(\Theta)}\Big)}{\sqrt{\frac{\csc(\Theta)k}{g}}} dt\\
  d &= \frac{\log(\cosh\Big(t\sqrt{kg\sin(\Theta)}\Big))}{\sqrt{kg\sin(\Theta)}\sqrt{\frac{\csc(\Theta)k}{g}}}\\
  d &= \frac{\log(\cosh\Big(t\sqrt{kg\sin(\Theta)}\Big))}{\sqrt{\frac{kg}{\csc(\Theta)}}\sqrt{\frac{\csc(\Theta)k}{g}}}\\
 d &= \frac{\log(\cosh\Big(t\sqrt{kg\sin(\Theta)}\Big))}{k}\\    
  kd &= \log(\cosh\Big(t\sqrt{kg\sin(\Theta)}\Big))\\
  e^{kd} &= \cosh\Big(t\sqrt{kg\sin(\Theta)}\Big)\\
  \cosh^{-1}(e^{kd}) &= t\sqrt{kg\sin(\Theta)}\\
  \frac{\cosh^{-1}(e^{kd})}{\sqrt{kg\sin(\Theta)}} &= t\\        
\end{align*}

>>>>

\usepackage{graphicx}
\usepackage{amsmath}

@@

@@

\title{Classical Mechanics Assignment X}
\author{Elliott Capek}
\titlespacing{\section}{0pt}{0pt}{5pt} % Spacing around titles

@@

\section{Problem One}
\textbf{Consider an object that is thrown vertically up with initial speed $v_0$ in a linear medium.} \\ \\

@@

\begin{align*}
  v'(t) = -g - bv\\

\end{align*}

@@

\textbf{c. Show that the limiting case for very small drag coefficient coincides with the solution for the frictionless motion.}

@@

\section{Problem Two}
\textbf{A point mass of mass m slides down an inclined plane under the influence of gravity. If the motion is resisted by a force F=kmv2, show that the time required to move a distance d after starting from rest is:}

\begin{equation*}
  t = \frac{\cosh^{-1}(e^{kd}}{\sqrt{kg\sin(\Theta)}}\\
\end{equation*}

@@
